Thesis: draft

### 2021-03-23 draft.tex
small change in stubborn section

@@

	\item If $0 < r_i < 1$, the node has some resistance but can still be convinced to switch to the other opinion, even though he/she will be less likely to do so 

>>>>

% DON'T FORGET: popular text somewhere!!

@@

	\item If $0 < r_i < 1$, the node has some resistance but can still be convinced to switch to the other opinion, even though he/she will be less likely to do so. A uniform random number $f$ between 0 and 1 is drawn. If $f > r_i$, the node will update his/her opinion; if $f \leqslant r_i$, the node is not convinced and keeps his/her own opinion 
